A Continuous Occlusion Model for Road Scene Understanding

### 2016-01-20 CVPR16/rebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2072} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{A Continuous Occlusion Model for Road Scene Understanding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that, following similar guidelines to previous CVPR conferences, the rebuttal is meant to address only the reviewers' comments and questions. It is not intended to add new material (theorems, algorithms, experiments) which was not included in the original submission. You may optionally add a figure, graph or proof to your rebuttal, but only to better illustrate your answer to the reviewers' comments. These additions must be minimal (as they are meant to address only the reviewers' comments). You must not use the rebuttal to add any new results or contributions.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{rebuttal}
}

\end{document}

### 2016-01-22 CVPR16/rebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables

\usepackage{color}
\newcommand{\hili}[1]{\colorbox{yellow}{#1}}

@@

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\input{preamble}
\newcommand{\xmin}{x_\text{min}}
\newcommand{\ymin}{y_\text{min}}
\newcommand{\xmax}{x_\text{max}}
\newcommand{\ymax}{y_\text{max}}
\DeclareMathOperator*{\argmin}{\arg\min}
\input{Source/drawingslib}

@@

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{A Continuous Occlusion Model for Road Scene Understanding}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

As suggested by Reviewers 1 and 2, we have added Table~\ref{tab:notations} for improving the exposition of our methods. In addition to feature tracks and detection bounding boxes, we use camera poses and 3D object bounding boxes (estimated respectively using SFM and assuming detection bounding boxes lie on the ground with priors on object dimensions) for computing object-point association probabilities and initializing 3D object localization methods.

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
& Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
					   	& $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
						& $\bomega^c(t)$ & Orientation of camera at time $t$ \\
						& $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
					    & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
						& $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of time $t$) \\

\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
						& $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
					    & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
						& $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
\hline
\end{tabular}
\caption{Notation of input and output.}
\label{tab:notations}
\end{table}

Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association. Reviewer 2 further said that we demonstrated only for a single but important object category (car), which is because it is the only one that we have ground truth data for (KITTI dataset), and there are very few obstacles to apply our methods to other categories as long as we have feature tracks and detection bounding boxes.

Regarding the complicated graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them. Future work will invest in speeding up the inference. In the following, we will respond to each reviewer's comments:

\section{Reviewer 1}

We thank Reviewer 1 for the suggestion of including the errors corresponding to the initial estimates in Table~\ref{tab:localization}, which clearly shows the benefits of energy minimization.

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
Energy & t & dim \\
\hline
\hline
Baseline & \hili{XXX} & \hili{XXX} \\
Initialization & \hili{XXX} & \hili{XXX} \\
$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
& 3.95  & 1.72\\        
$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
& 4.81  & 2.16\\        
$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
& 4.05  & {\bf 1.59}\\        
$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
& {\bf 3.24}  & 2.16\\
\hline
\end{tabular}
\caption{Localization experiment results.}
\label{tab:localization}
\end{table}

Equation 4: we use gradient occupancy vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero. We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$. Please refer to Figure 2 for an illustration of reflection probability.

We compute the normalization factor $Z'$ in Equation 13 numerically using importance sampling.

\section{Reviewer 2}

Instead of using binary functions, we model objects by translucent functions, which not only accounts for object shape uncertainty but also allows a continuous occlusion model that remains amenable to continuous optimization tools.

Section 4.2: our apologies, we have included all objects in the first equation as follows:
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i \} | \{\bu_j(t)\} , \{\bb{i}\} )} = -Z + \\ 
  \lambda_t \sum_{t=s_i}^{e_i} \EnergyTrack
  + 
  \lambda_d \sum_{t=s_i}^{e_i} \sum_{i=1}^N \EnergyBBox
  + 
  \lambda_{\text{dyn}} \sum_{i=1}^N \EnergyDyn
  + 
  \lambda_{\text{size}} \sum_{i=1}^N \EnergySize
  \enspace,
\end{multline*}
and have excluded object poses from the previous time step in Equation 19 as below:
\begin{align*}
\Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align*}

The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS. Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be removed by object tracking [2]. We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames. After running object tracking [2], there are total \hili{XXX} objects survived.

In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (though they are only for depth ordering). The crucial question now is how to probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is in fact a principle way to do that same thing.

In localization experiments, we have tried [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 mins for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on priors on object dimensions for unobservable dimensions. We have included the results of this baseline in Table~\ref{tab:localization}.

\section{Reviewer 3}

Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth. Alternatively, this information is given by the reflection probability. Therefore, a combination of transmission and reflection probabilities is more suitable for explaining the image observations.

Regarding the concern about the superiority of our method in Figure 5, we focus on a probabilistic method to incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).

### 2016-01-22 CVPR16/rebuttal.tex

\section{Reviewer 1}

We thank Reviewer 1 for the suggestion of including the errors corresponding to the initial estimates in Table~\ref{tab:localization}, which clearly shows the benefits of energy minimization.

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
Energy & t & dim \\
\hline
\hline
Baseline & \hili{XXX} & \hili{XXX} \\
Initialization & \hili{XXX} & \hili{XXX} \\
$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
& 3.95  & 1.72\\        
$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
& 4.81  & 2.16\\        
$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
& 4.05  & {\bf 1.59}\\        
$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
& {\bf 3.24}  & 2.16\\
\hline
\end{tabular}
\caption{Localization experiment results.}
\label{tab:localization}
\end{table}

Equation 4: we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero. We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$. Please refer to Figure 2 for an illustration of reflection probability.

@@

\section{Reviewer 2}

Instead of using binary functions, we model objects by translucent functions, which not only accounts for object shape uncertainty but also allows a continuous occlusion model that remains amenable to continuous optimization tools.

Section 4.2: our apologies, we have included all objects in the first equation as follows:
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i \} | \{\bu_j(t)\} , \{\bb{i}\} )} = -Z + \\ 
  \lambda_t \sum_{t=s_i}^{e_i} \EnergyTrack
  + 
  \lambda_d \sum_{t=s_i}^{e_i} \sum_{i=1}^N \EnergyBBox
  + 
  \lambda_{\text{dyn}} \sum_{i=1}^N \EnergyDyn
  + 
  \lambda_{\text{size}} \sum_{i=1}^N \EnergySize
  \enspace,
\end{multline*}
and have excluded object poses from the previous time step in Equation 19 as below:
\begin{align*}
\Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align*}

The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS. Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be filtered out by object tracking [2]. We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames. After running object tracking [2], there are total \hili{XXX} objects survived.

In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (despite simple depth ordering). The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.

In localization experiments, we have tested [33] on a few images and it has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 mins for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have added the suggested baseline which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions. We have included the results of this baseline in Table~\ref{tab:localization}.

@@

\section{Reviewer 3}

Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth. Alternatively, this information is given by reflection probability. Therefore, a combination of transmission and reflection probabilities is more suitable for explaining image observations.

Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33] which use CAD models).

### 2016-01-22 CVPR16/rebuttal.tex

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
& Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
					   	& $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
						& $\bomega^c(t)$ & Orientation of camera at time $t$ \\
						& $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
					    & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
						& $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of time $t$) \\

\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
						& $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
					    & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
						& $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
\hline
\end{tabular}
\caption{Notation of input and output.}
\label{tab:notations}
\end{table}

Reviewers 1 and 2 mentioned the coarse representation of objects (3D ellipsoids), our aim is to balance between the ease of analytical formulations and the practical requirements of object-point association. Reviewer 2 further said that we demonstrated only for a single but important object category (car), which is because it is the only one that we have ground truth data for (KITTI dataset), and there are very few obstacles to apply our methods to other categories as long as we have feature tracks and detection bounding boxes.

Regarding the complex graphical model and computational aspect, our current work focuses on the flexibility of our occlusion model, and there are many potential applications while object localization is one of them. Future work will invest in speeding up the inference. In the following, we will respond to each reviewer's comments:

@@

\section{Reviewer 1}

We thank Reviewer 1 for the suggestion of including the errors corresponding to the initial estimates in Table~\ref{tab:localization}, which clearly shows the benefits of energy minimization.

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
Energy & t & dim \\
\hline
\hline
Baseline & \hili{XXX} & \hili{XXX} \\
Initialization & \hili{XXX} & \hili{XXX} \\
$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
& 3.95  & 1.72\\        
$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
& 4.81  & 2.16\\        
$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
& 4.05  & {\bf 1.59}\\        
$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
& {\bf 3.24}  & 2.16\\
\hline
\end{tabular}
\caption{Localization experiment results.}
\label{tab:localization}
\end{table}

In Equation 4, we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero. We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$ (our apologies, we will fix this). Please refer to Figure 2 for an illustration of reflection probability.

@@

Section 4.2: our apologies, we have included all objects in the first equation as follows:
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i \} | \{\bu_j(t)\} , \{\bb{i}\} )} = -Z + \\ 
  \lambda_t \sum_{t=s_i}^{e_i} \EnergyTrack
  + 
  \lambda_d \sum_{t=s_i}^{e_i} \sum_{i=1}^N \EnergyBBox
  + 
  \lambda_{\text{dyn}} \sum_{i=1}^N \EnergyDyn
  + 
  \lambda_{\text{size}} \sum_{i=1}^N \EnergySize
  \enspace,
\end{multline*}
and have excluded object poses from the previous time step in Equation 19 as below:
\begin{align*}
\Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align*}

The number of objects is known a priori in our occlusion model (given by object tracking [2]) and is also provided to other methods such as BBox and RAS. Outlier feature tracks usually have high reprojection errors and hence low object-point association probabilities while outlier detection bounding boxes are likely to be filtered out by object tracking [2]. We use \hili{XXX} sequences from KITTI dataset, which have total \hili{XXX} frames. After running object tracking [2], there are total \hili{XXX} objects survived.

In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (despite simple depth ordering). The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.

In localization experiments, we have tested [33] on a few images. It has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 minutes for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have included in Table~\ref{tab:localization} the suggested baseline, which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.

In a sense Equation 4 reverts to a (squared) Lambertian reflection, which is basically a dot product between surface normal and light direction.

We thank Reviewer 3 for pointing us to recent works on visibility modeling of scenes/point clouds and holistic scene understanding with fast MRF inference. These ideas look useful and we will cite these papers if accepted.

@@

\section{Reviewer 3}

Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth. Alternatively, this information is given by reflection probability. Therefore, a combination of transmission and reflection probabilities is more suitable for explaining image observations.

Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33]).

About the localization experiment results in Table~\ref{tab:localization}, we observe that using occlusion modeling for feature tracks and detection bounding boxes individually leads to higher translation errors, however using occlusion modeling for both of them yields lower translation errors. This is probably due to the values of the parameters that we empirically chose.

For all other minor comments/typos, we will fix them if accepted.

### 2016-01-22 CVPR16/rebuttal.tex

In object-point association experiments, the baseline method (BBox) uses 3D bounding boxes (despite simple depth ordering). The crucial question is how we can probabilistically weigh points closer to the boundary of the 3D bounding box less than points inside the box and our occlusion model is a principle way to implement that idea.

In localization experiments, we have tested [33] on a few images. It has higher localization accuracy than our method, which is mostly due to its detailed shape model. However, it needs a database of CAD models, takes about 30 minutes for inference on a single image, and is a discrete model which is not suitable for continuous optimization tools. Alternatively, we have included in Table~\ref{tab:localization} the suggested baseline, which robustly fits a 3D bounding box on the reconstructed point cloud (by SFM within detection bounding boxes) and relies on object dimension priors for unobservable dimensions.

In a sense Equation 4 reverts to a (squared) Lambertian reflection, which is basically a dot product between surface normal and light direction.

We thank Reviewer 2 for pointing us to recent works on visibility modeling of scenes/point clouds and indoor scene understanding with fast MRF inference. These ideas look useful and we will cite these papers if accepted.

@@

\section{Reviewer 3}

Transmission probability only indicates whether a ray is transmissible to a particular depth but does not provide information on which object obstructs the ray at that depth. Alternatively, this information is given by reflection probability. Therefore, a combination of transmission and reflection probabilities is more suitable for explaining image observations.

Regarding the concern about the superiority of our method in Figure 5, we focus on a principle method to probabilistically incorporate all available information for occlusion reasoning and it is not provided by previous works (in a sense this was also the goal of [32][33]).

About the localization experiment results in Table~\ref{tab:localization}, we observe that using occlusion modeling for feature tracks and detection bounding boxes individually leads to higher translation errors, however using occlusion modeling for both of them yields lower translation errors. This is probably due to the values of parameters that we empirically chose.

We will fix all other minor comments/typos if accepted.

### 2016-01-23 CVPR16/rebuttal.tex

\section{Reviewer 1}

We thank Reviewer 1 for the suggestion of including the errors corresponding to the initial estimates in Table~\ref{tab:localization}, which clearly shows the benefits of energy minimization.

\begin{table}\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
Energy & t & dim \\
\hline
\hline
Baseline & \hili{XXX} & \hili{XXX} \\
Initialization & \hili{XXX} & \hili{XXX} \\
$\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
& 3.95  & 1.72\\        
$\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
& 4.81  & 2.16\\        
$\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
& 4.05  & {\bf 1.59}\\        
$\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
& {\bf 3.24}  & 2.16\\
\hline
\end{tabular}
\caption{Localization experiment results.}
\label{tab:localization}
\end{table}

In Equation 4, we use gradient vector $\nabla {f^i_{occ}}(\bx_j)$ since we want reflection probability to be high near object borders, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off, and squaring allows the function to be smooth near zero. We normalize $P^{ij}_{\textit{reflection}}(\lambda)$  with respect to different $\lambda$ (our apologies, we will add a normalization factor). Please refer to Figure 2 for an illustration of reflection probability.

### 2016-01-25 CVPR16/Rebuttal2/Source/_BACKUP_intro.tex
draft rebuttal

As a two-dimensional (2D) projection of the three-dimensional (3D) world, image formation is associated with a loss of information. This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint. In recent years, we have seen remarkable progress in various aspects of scene understanding, such as structure from motion (SFM) and object detection. However, occlusions still present a challenge, with the difficulty of physically modeling them being a major bottleneck. 
%Prior works have considered occlusions in 2D or through discrete occluder patterns

\begin{figure}[!!t]
\begin{center}
\includegraphics[width=\linewidth]{graphics/figure1.png}
\end{center}
\vspace{-0.6cm}
\caption{\small We propose an occlusion model in 3D that is physically-inspired and continuous. Given object detection and SFM point tracks, our unified model probabilistically assigns point tracks to objects and reasons about object detection scores and bounding boxes. It uniformly handles static and dynamic objects, thus, outperforms motion segmentation for association problems. We also demonstrate occlusion-aware 3D localization in road scenes.}
\label{fig:page1}
\vspace{-0.4cm}
\end{figure}

Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D. Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids. In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera. This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions. This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns or models that are not physically interpretable \cite{Hsiao_Herbert_2012,Pepik_etal_2013,Xiang_Savarese_2013,Zia_etal_2013,Zia_etal_2014}.

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for uniformly modeling the association of SFM point tracks with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate the application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}. But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

Another potential application of our proposed model is towards 3D localization in road scenes. Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either. In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs. Our model is continuous, so remains amenable to the use of continuous optimization tools.

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
\item Unified occlusion handling for point tracks in SFM and bounding boxes and detection scores in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}

@@

%The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work. Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding. Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization. Finally, we conclude in Section~\ref{sec:conclusions}.

>>>>

As a 2D projection of the 3D world, image formation is often associated with a loss of information. This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint. In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion and object detection. However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck. 
%Prior works have considered occlusions in 2D or through discrete occluder patterns

Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D. Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids. In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera. This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions. This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for modeling the association of 3D structure from motion points with static or dynamic objects, as well as modeling object detection scores in applications like 3D localization. We demonstrate application of our formulations for road scenes from the KITTI dataset.

Assigning 2D point tracks to independently moving, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing moving objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}. But motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

As another important contribution, we examine the applicability of our proposed model to 3D localization in autonomous driving. Prior works such as \cite{Song_Chandraker_2014} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either. In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs. Our model is continuous, so remains amenable to the use of continuous optimization tools.

To summarize, our main contributions are:
\begin{itemize}
\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and 3D.
\item Unification of occlusion handling in different applications, such as points tracks in SFM and object bounding boxes in detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{itemize}

@@

The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work. Section~\ref{sec:setup} describes the proposed continuous occlusion model for road scene understanding. Section~\ref{sec:experiments} presents detailed experiments for point-to-object association and 3D localization. Finally, we conclude in Section~\ref{sec:conclusions}.
